MSHS COVID-19 Vaccinations

### 2021-05-20 Evening-Huddle-Stats.Rmd
Update reference file

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-05-03.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-05-03.xlsx"),
                           sheet = "Pod Mappings Simple")

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-05-20.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-05-20.xlsx"),
                           sheet = "Pod Mappings Simple")
